Enforced Invariant Confluence

### 2018-03-29 doc/paper/sections/invariant_confluence.tex
Finished invariant-confluence section.

% - define invariant confluence
%   - define system model
%   - define expression based system model
%   - define invariant confluence
%   - Give example with two integers

% TODO: Give a footnote about the difference between this definition and the original definition.

>>>>

We say an expression $e$ is \defword{$\sTIreachable{}$} if it corresponds to a
valid execution of our system model. Formally, we define $\sTIreachable{e}$ to
be the smallest predicate that satisfies the following equations:
\begin{itemize}
  \item
    $\sTIreachable{s_0}$.
  \item
    For all expressions $e$ and for all transactions $t$ in the set $T$ of
    transactions, if $\sTIreachable{e}$ and $I(t(e))$, then
    $\sTIreachable{t(e)}$.
  \item
    For all expressions $e_1$ and $e_2$, if $\sTIreachable{e_1}$ and
    $\sTIreachable{e_2}$, then $\sTIreachable{e_1 \join e_2}$.
\end{itemize}
Similarly, we say a state $s \in S$ is $\sTIreachable{}$ if there exists a
$\sTIreachable{}$ expression $e$ that evaluates to $s$.

Finally, we say $O$ is \defword{invariant-confluent with respect to $s_0$, $T$,
and $I$}, abbreviated \defword{\sTIconfluent{}}, if all reachable states
satisfy the invariant: $\setst{s \in S}{\sTIreachable{s}} \subseteq I$.
